\begin{abstract}
	
% MOTIVATION
Natural language processing (NLP) is a family of technologies that can disruptively reshape human-machine interaction, data-driven decision making and daily exploration of knowledge by humans.
%
One of the most representative and widely studied NLP application is question-answering (Q\&A).
%
With the fast growing diffusion of semantic web and advancement in NLP technologies, Q\&A systems will be one of the most important interface to knowledge.


% PROBLEM STATEMENT
Since it is not possible to develop a single ontology to effectively capture the whole knowledge, it is necessary to develop Q\&A systems that can easily adapt to distinct ontologies and lexicons.


% APPROACH
In this work we describe Ontoqa, a Q\&A web and standalone application which aims to achieve this ambitious goal.
%
The proposed solution leverages ontology-driven NLP through the use of the LTAG/DUDES model and a greedy parsing algorithm aiming to reduce both the syntactic and semantic search space.
%
%
% RESULTS
The experimental results show that our system can answer the benchmark questions, with good performance with respect to both response-time and memory usage. 
%
%
% CONCLUSIONS
Our work shows that ontology alignment through the LTAG/DUDES model permits 
high modularization and generalization of the NLP process.
%
Furthermore, such a model suits well to the design of parsing algorithms that can effectively minimize both the syntactic and semantic search space.
 

\end{abstract}
