\section{Parsing}
\label{sec:parsing}

The parser is responsible to generate the LTAG/DUDES representation of a question expressed in natural language\footnote{we have restricted our research to the English language.}. 
%
The parser takes in input a natural language sentence $S$, the grammar $G$ and the ontology $O$ \footnote{as stated in the previous sections, we assume that $G$ is aligned to $O$ through a lexicon.}.
%
In particular, it leverages $G$ to recognize lexical entries in $S$, and $O$ to execute reasoning steps for disambiguation during parsing.
%
The generated DUDES is finally used by the application control layer to compose the SPARQL query to be submitted to the ontology.


The parser has been designed addressing two main requirement: \textit{correctness} and \textit{minimization of the syntactic/semantic search space}, which is the most critical aspect to achieve better performance.
%
The previous requirements have been met through a parsing algorithm that is (i) deterministic (ii) greedy and (iii) particularly focused on structural aspects of LTAG.
Furthermore, the performance boost in terms of response-time have been achieved though the minimization of the interaction with the ontology.

The parsing process is carried out by two main functional components: 
(i) the \texttt{Tokenizer}, which recognizes in the sentence textual patterns that can be traced back to grammar entries, and sequentially emit them as tokens, and 
(ii) the \texttt{Parser} itself, which consumes these tokens, composing them to make LTAG/DUDES compositions\footnote{both substitutions and adjunctions.}.

In Section~\ref{sec:parsing-tokenization} and Section~\ref{sec:parsing-algorithm} we describe and motivate the architectural choices and the pseudocode realizing tokenization and the parsing algorithm, respectively.
%
Furthermore, in Section~\ref{sec:parsing-ambiguities} and Section~\ref{sec:parsing-support-dudes-composition} we show how our parser solve ambiguities through reasoning and how it supports DUDES composition though main variables mappings.

\input{sec/parsing-tokenization}
\input{sec/parsing-algorithm}
\input{sec/parsing-ambiguities}
\input{sec/parsing-main-variables-mapping}